---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
```

Goal: Calculate a range of K values for use in our fisheries modeling

Look at stock catch data, mean catch data:
```{r}
stock <- read_csv(file.path(here(),"/globalprep/fis/v2019/output/stock_catch.csv"))
mean_catch <- read_csv(file.path(here(),"/globalprep/fis/v2019/output/mean_catch.csv"))
fis_catch <- read_csv(file.path(here(),"/globalprep/fis/v2019/output/FP_fis_catch.csv"))

```

Looks like the stock catch data will be the best since mean catch is aggregated by family and I'm interested in a broad range of K estimates.

Write a function to estimate MSY from catch and to estimate K from MSY
Based on Mangin et al 2018
```{r}
#Estimate MSY:
msy <- function(catch){
  1.78 * (10 ^ -0.8644 + (1.0976 * log10(catch)))
}

#Estimate K 
K_est <- function(msy, g, phi){
  (msy * ((phi + 1) ^ (1/phi))) / g
}

```

Use this equation to mutate a column on the dataframe that includes MSY:
```{r}
#extract vector of catch values to feed into the MSY equation:
catch_val <- stock$tons

#Feed that vector through the msy function
msy_est <- msy(catch = catch_val)

#Mutate a column for msy values into the stock dataframe:
stock_edit <- stock %>% 
  mutate(msy = msy_est)
```

Minor issue... I need g values to run the K calculation and I don't have those for these stocks... 